Space-time plots

### 2017-05-11 Rmd/space-time.Rmd
Revision through new figure 3, and updates to text. Culling out old code that does not appear or is used in analysis (e.g. normal bootstrapping code, polygon version of plots)

```{r, eval=FALSE}
# p <- c(0.64, 0.84, 0.53, 1.21)  # from calibration.Rmd
# p <- c(0.58, 0.82, 0.99, 1.24)  # from calibration.Rmd
##     plot_res   n_sites   act_ext   eff_ext t_btwn_samp  act_dur   eff_dur
## 1: 0.5769693 0.3821107 0.7196559 0.4049972     1.01134 1.253045 0.5284913
p <- c(0.58, 0.75, 0.50, 1.01, 1.23, 0.59)  # from calibration.Rmd

@@

# hdat_bsdt <- lapply(1:length(vs), function(x) { # x <- 1
#   mat <- do.call(rbind, lapply(1:length(hdat_bs), function(y) {
#     hdat_bs[[y]][[x]]
#   }))
#   data.table(mat)
# })

# setnames(hdat_bsdt, names(hdat_bsdt), as.character(aaxis1$logres))

# hist(hdat$res, breaks = aaxis1$logres)
# hist(log10(datf$plot_res), breaks = resbrks)
# hist(log10(datf$plot_res), breaks = resbrks)

## Ordinary histograms
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
# plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- c(25, 40)
# pdf("paper/figures/hists.pdf", width = 7, height = 2.5)
pdf("paper/figures/hists.pdf", width = 5, height = 5)
par(mfrow = c(2, 2), mar = c(4.5, 1, 1, 1), oma = c(2, 3, 0, 0))
# resolution
h <- hist(hdat$res, breaks = aaxis1$logres, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial resolution", 
     ylim = c(0, yl[1]), main = "", col = reds[4], cex.lab = cxl)
axis(1, at = aaxis1$logres, labels = alab1, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)
mtext("A", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# extent
h <- hist(hdat$ext, breaks = aaxis2$logarea, plot = FALSE)
# h <- hist(hdat$aext, breaks = c(-6, aaxis2$logarea), plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial extent", ylim = c(0, yl[1]), 
     main = "", col = reds[6], cex.lab = cxl)
axis(1, at = aaxis2$logarea,
     labels = alab2,
     # labels = c(expression(paste(NULL<="0.01m"^2)), expression(paste(0.1, m^2)),                 alab2[-1]), 
     las = 2, cex.axis = cxa,
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("B", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# interval
tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$int, breaks = taxis1$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Sampling interval", ylim = c(0, yl[2]), 
     main = "", col = blues[4], cex.lab = cxl)
axis(1, at = tax, labels = tlab1[-10], las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, -0.34))
mtext("C", side = 3, line = sfigl, cex = 0.8, adj = 0.05)
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)

# duration
# tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$dur, breaks = taxis2$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Temporal duration", ylim = c(0, yl[2]),      main = "", col = blues[6], cex.lab = cxl)
axis(1, at = taxis2$logdays, labels = tlab2, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("D", side = 3, line = sfigl, cex = 0.8, adj = 0.05)
dev.off()

### Bootstrapped histograms (now main figure)
qtf <- function(x) c(mean(x), quantile(x, probs = c(0.025, 0.975))) # quant f
xlabs <- c("Spatial resolution", "Spatial extent", "Sampling interval", 
           "Temporal duration")
# axes <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
#              "tax1" = taxis1$logdays, "tax2" = taxis2$logdays)
axes2 <- list("aax1" = aaxis1$logres, "aax2" = aaxis2$logarea, 
              "tax1" = c(taxis2$logdays[-c(10:11)],
                         mean(taxis2$logdays[c(10:11)])), 
              "tax2" = taxis2$logdays)
# axlabs <- list(alab1, c(expression(paste(NULL<="0.01m"^2)),
#                         expression(paste(0.1, m^2)), alab2[-c(1:2)]),
axlabs <- list(alab1, alab2, tlab1[-10], tlab2)
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
# plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- 35
cols <- c(reds[c(4, 6)], blues[c(4, 6)])

@@

# pdf("paper/figures/hists.pdf", width = 7, height = 2.5)
pdf("paper/figures/hists_bs.pdf", width = 5, height = 5)
par(mfrow = c(2, 2), mar = c(4.5, 1, 1, 1), oma = c(2, 3, 0, 0))

@@

Statistics associated with Figure 1: percentage of observations falling within different scale ranges, and associated with different observational methods
```{r}
# res
# hdatst <- hdatstat[[1]]$density
hdatst <- hdatstat_bt$res$mu
l <- length(hdatst)
sum(hdatst[4:6])  # 53 % between 10cm^2 and 1 m^2
sum(hdatst[1:6])  #  67% < 1m^2
sum(hdatst[7:10]) # 24 % between 1 m^2 and 1 ha
sum(hdatst[11:(l)]) # 9 % 1-10000 ha
# dat[plot_res >= 10000^2]

@@

# points(resdat3$x[which(datf$st == 4)], resdat3$y[which(datf$st == 4)])
# points(resdat3$x[which(datf$st == 1)], resdat3$y[which(datf$st == 1)])

@@

# densities
# resolution
rres3 <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat3, 1)
rres3 <- (rres3 / cellStats(rres3, sum)) * 100
# rng <- range(rres3[is.finite(rres3)])
# bwidth <- (rng[2] - rng[1]) / 30
# brks <- seq(rng[1], rng[2], bwidth)
# brklabs <- seq(0, 0.12, 0.02)#round(brks[seq(1, length(brks), 5)], 2)
# brklabs <- seq(0, 0.1, 0.02)#round(brks[seq(1, length(brks), 5)], 2)

# extent
rext3 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat3, 1)
rext3 <- (rext3 / cellStats(rext3, sum)) * 100
# rng <- range(rext3[is.finite(rext3)])
# # rng[2] <- 0.1
# bwidth <- (rng[2] - rng[1]) / 30
# brks2 <- seq(rng[1], rng[2], bwidth)
# brklabs2 <- brklabs #round(brks2[seq(1, length(brks2), 3)], 2)

@@

### Figure 3
```{r}
datf[, plot(log10(eff_ext), log10(act_ext))]
datf[, plot(log10(act_dur), log10(eff_dur))]
datf[log10(eff_dur) < log10(act_dur)]
calr[log10(eff_dur) < log10(act_dur)]
dat[DOI == "10.1007/s10021-013-9684-x"]
cal[DOI == "10.1007/s00442-010-1713-2"]
dat[DOI %in% datf[log10(eff_ext) < log10(act_ext), DOI]]
dat[DOI %in% datf[log10(eff_ext) < log10(act_ext), DOI]]
datf[log10(eff_ext) < log10(act_ext), ]
datf[DOI == "10.1111/j.1466-8238.2011.00658.x", 
     .(log10(round(eff_ext)), log10(round(act_ext)))]
datf[DOI == "10.1111/j.1466-8238.2011.00658.x", 
     .(round(eff_ext), round(act_ext))]

# actual versus effective duration
kdat <- bootp_dt  # bootstrap
# tempdat2 <- data.table(x = log10(kdat$act_dur), y = log10(kdat$eff_dur))
tempdat2 <- data.table(x = log10(kdat$eff_dur), y = log10(kdat$act_dur))
dinds <- kdat[, which(t_btwn_samp == 365 * 10000)]  # drop unreplicated obs
tempdat2 <- tempdat2[-dinds, ]
tempdat2 <- tempdat2[!is.na(x) & !is.na(y)] # cut out null values
tempdat2[, n := 1]  # set up count column
tx <- range(taxis2$logdays)
tx <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[x < tx[1], x := tx[1]]
tempdat2[x > tx[2], x := tx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[y < tx[1], y := tx[1]]
tempdat2[y > tx[2], y := tx[2]]
coordinates(tempdat2) <- ~x + y

@@

pdf("paper/figures/act_v_eff.pdf", width = 7, height = 3)
par(mfrow = c(1, 2), mar = c(4.5, 4.5, 0.3, 3), oma = c(0, 0, 0.2, 1), 
    mgp = c(2, 0.25, 0))

@@

# Bootstrap version
vs1 <- c("eff_ext", "act_ext", "eff_dur", "act_dur")
vs2 <- c("eext", "aext", "edur", "adur")
hdat_bs2 <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  # print(x)
  DT <- bootperturb[[x]]
  edb <- DT[, lapply(.SD, log10), .SDcol = c("eff_ext", "act_ext")]
  # edb <- edb[eff_ext >= act_ext, ]  # drop eff_dur < act
  setnames(edb, c("eff_ext", "act_ext"), c("eext", "aext"))
  edb[, dif := eext - aext]
  # elm <- edb[, lm(dif ~ aext)]
  # preds <- predict(elm, newdata = data.frame(aext = extdum))
  # plot(extdum, preds)

  tdb <- DT[t_btwn_samp != 365 * 10000, lapply(.SD, log10), 
            .SDcol = c("eff_dur", "act_dur")]
  # tdb <- tdb[eff_dur >= act_dur, ]  # drop eff_dur < act
  setnames(tdb, c("eff_dur", "act_dur"), c("edur", "adur"))
  print(paste(edb[, .N], tdb[, .N]))
  tdb[, dif := edur - adur]
  # tlm <- tdb[, summary(lm(dif ~ adur))]
  return(list("edb" = edb, "tdb" = tdb, #"elm" = elm, "tlm" = tlm, 
              "Ns" = c(edb[, .N], tdb[, .N])))
})

# calculate box statistics
# Extent differences
eint <- aaxis2$logarea
edif_int <- rbindlist(lapply(hdat_bs2, function(y) {  # y <- hdat_bs2[[2]]
  dd <- copy(y$edb[!is.na(aext)])
  dd[aext < ex[1], aext := ex[1]]  # set to min
  # dd[, list("int" = findInterval(aext, eint), "dif" = dif)]
  dd[, int := findInterval(aext, eint)]
  # dd[, list("dif" = mean(dif, na.rm = TRUE), "N" = .N), by = int][order(int)]
}))

ints <- sort(edif_int[, unique(int)])
ebox <- lapply(ints, function(x) edif_int[int == x, lmisc::box_stats(dif)])
pctobs <- sapply(ints, function(x) edif_int[int == x, .N])
ewgt <- pctobs / sum(pctobs)
ewgt * 100
ealphs <- (ewgt - min(ewgt)) / diff(range(ewgt))

# temporal differences
dint <- taxis2$logdays[-5]
tx <- range(dint)
ddif_int <- rbindlist(lapply(hdat_bs2, function(y) {  # y <- hdat_bs2[[2]]
  dd <- copy(y$tdb[!is.na(adur)])
  dd[adur < tx[1], adur := tx[1]]  # set to min
  dd[adur > tx[2], adur := tx[2]]  # set to max
  dd[, int := findInterval(adur, dint)]
}))

dints <- sort(ddif_int[, unique(int)])
tbox <- lapply(dints, function(x) ddif_int[int == x, lmisc::box_stats(dif)])
pctobs <- sapply(dints, function(x) ddif_int[int == x, .N])
dwgt <- pctobs / sum(pctobs)
dalphs <- (dwgt - min(dwgt)) / diff(range(dwgt))

pdf("paper/figures/act_v_eff_diff.pdf", width = 7, height = 4)
par(mfrow = c(1, 2), mar = c(4, 0, 1, 0.75), oma = c(0, 3, 0, 0))
bx <- rowMeans(cbind(eint[-length(eint)], eint[-1]))
cols <- sapply(ealphs, function(x) rgb(0, 0.1, 1, alpha = x))
# plot(1:length(cols), col = lcols, pch = 20)
plot(ex, c(0, 14), pch = "", xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     mgp = c(3, 0.5, 0), tcl = -0.2, xaxs = "i")
# grid(lty = 1, col="gray")
# polygon(c(ex, rev(ex), ex[1]), c(-1, -1, 15, 15, -1), col = "grey90")
for(i in 1:length(ebox)) {
  boxplot_v(bx[i], y = ebox[[i]], n = 1.75, whiskhgt = 1.5, bfill = cols[i])
} 
axis(1, at = eint, labels = alab2, las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
axis(2, at = seq(0, 14, 2), las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
mtext("Actual Extent", side = 1, line = 3)
mtext("Difference Magnitude:", side = 2, line = 2)
mtext("Effective minus Actual", side = 2, line = 1)
# xs <- seq(2, 10, by = (10 - 2) / (length(ealphs)))
# ealphss <- sort(ealphs, decreasing = TRUE)
# lcols <- sapply(ealphss, function(x) rgb(0, 0.1, 1, alpha = x))
# rect_shade(xs, y = c(13, 14), fillcol = lcols, linecol = "grey")
# text(xs, rep(13, length(xs)), sort(round(ewgt * 100), decreasing = TRUE),
#      srt = 90)

bx <- rowMeans(cbind(dint[-length(dint)], dint[-1]))
bd <- abs(dint[-length(dint)] - dint[-1])
cols <- sapply(dalphs, function(x) rgb(1, 0, 0.1, alpha = x))
# plot(1:length(cols), col = cols, pch = 20)
plot(tx, c(0, 14), pch = "", xlab = "", ylab = "", xaxt = "n", 
     mgp = c(3, 0.5, 0), tcl = -0.2, yaxt = "n")
for(i in 1:length(tbox)) {
  boxplot_v(bx[i], y = tbox[[i]], n = 0.9, inhgt = bd[i] * 10, whiskhgt = 0.5, 
            bfill = cols[i])
} 
axis(1, at = dint, labels = tlab2[-c(5)], las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
axis(2, at = seq(0, 14, 2), labels = rep("", 8), las = 2, tcl = -0.2, 
     cex.axis = cxa, mgp = c(3, 0.5, 0))
mtext("Actual Duration", side = 1, line = 3)
dev.off()

# # Calculate predictions from ensemble of regression coefficients
# extdum <- seq(-10, 10, 1)
# extpred <- do.call(rbind, lapply(1:nrow(hdat_bs2_elm), function(x) {
#   hdat_bs2_elm[x, 1] + hdat_bs2_elm[x, 2] * extdum
# }))
# extconf <- apply(extpred, 2, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))
# durdum <- seq(-5, 5, 1)
# durpred <- lapply(1:nrow(hdat_bs2_tlm), function(x) {
#   hdat_bs2_tlm[x, 1] + hdat_bs2_tlm[x, 2] * durdum
# })
# 
# plot(extmu[, 1], extmu[, 2], col = "grey", pch = 20)
# lines(extdum, extconf[1, ])
# lines(extdum, extconf[2, ])
# 
# 
# datf[, plot(log10(act_ext), log10(eff_ext - act_ext))]
# 
# log10(0.1 - 0.05)
# log10(0.1) - log10(0.05)
# a <- seq(0.1, 10, 0.1)^10
# mv <- runif(length(a), min = 1 - 0.4, max = 1 + 0.4)
# b <- sapply(1:length(a), function(x) a[x] * mv[x])
# plot(a, b)
# cbind(log10(a), log10(b), log10(a) - log10(b), a, b, log10(a - b))
# plot(log10(a), log10(b))
# 
# datf2 <- copy(datf[, .(act_ext, eff_ext)])
# chkd <- datf2[order(act_ext), {
#    ae = round(act_ext, 6)
#    ee = round(eff_ext, 2) 
#    aext = round(log10(act_ext), 2)
#    eext = round(log10(eff_ext), 2)
#    dif = round(ee - ae, 6)
#    dlog = round(log10(eff_ext) - log10(act_ext), 2)
#    logd = round(log10(eff_ext - act_ext), 2)
#    list("ae" = ae, "ee" = ee, "aext" = aext, "eext" = eext, 
#         "dif" = dif, "dlog" = dlog, "logd" = logd)
# }]
# chkd[1:100, ]
# chkd[, plot(aext, logd)]
# 
# plot(durmu[, 1], durmu[, 2])
# plot(extmu[, 1], extmu[, 2])

@@

```{r}
svars <- c("plot_res", "n_sites", "act_ext", "samp_dur",
           "t_btwn_samp", "act_dur")

sens <- gsub("\\\\", ";", dat$sensitivity)
sens <- gsub(", ", ";", gsub("; ", ";", sens))
sens <- tolower(sens)
sensl <- strsplit(sens, ";")
# unique(unlist(sensl))

sens2 <- gsub("plo_", "plot_", sens)  # fix this one
sens2 <- gsub("[[:blank:]]", "_", sens2)  # replace spaces with _

corrtab <- cbind(c("^res", "plo_res", "sample_area", "samples_area", 
                   "sampled area",
                   "t_btwn_samples", "t_btwn_sample", "t_btwn_samp_samp", 
                   "t_twn_samp", "t_btw_samp", "samp_duratiion", 
                   "sampling_duration", "sample_duration", 
                   "plot_resolution", "number_of_sites", 
                   "time_between_sampling", "plot_size", 
                   "time_between_samples", "samp_study", ":", " ", ";_"), 
                 c(svars[c(1, 1, 3, 3, 3, 5, 5, 5, 5, 5, 4, 4, 4, 1, 2,
                           5, 1, 5)], "samp;study", ";", ";", ";"))

for(i in 1:nrow(corrtab)) {
  sens2 <- gsub(corrtab[i, 1], corrtab[i, 2], sens2)
}
# gsub("[a-z]( )[a-z]", "_", sens[[228]])
# sens[[228]]
# sens2[is.na(sens2)]
sens2[is.na(sens2)] <- "none"
sensl2 <- lapply(1:length(sens2), function(x) strsplit(sens2[x], ";")[[1]])
# unique(unlist(sensl))
# unique(unlist(sensl2))

# create a sensitivity table
senst <- do.call(cbind.data.frame, lapply(svars, function(x) {
  v <- sapply(sensl2, function(y) ifelse(any(y == x), 1, 0))
  # ifelse(is.na(v), 0, v)
}))
colnames(senst) <- c("res", "n", "sarea", "sampd", "tbtwn", "studyd")

# add column for uncertainty about n repeats
# senst$nrep <- rep(0, nrow(senst))

# i <- 300:305
# sensl2[i]
# senst[i, ]

# apply fixes (mostly to account for observer omissions)

# 1. if samp_dur OR t_btwn_samp is uncertain, act_dur must also be. 
id <- which((senst$sampd == 1 | senst$tbtwn == 1) & senst$studyd == 0)
senst[id, "studyd"] <- 1

>>>>

```{r, eval=FALSE}
# p <- c(0.64, 0.84, 0.53, 1.21)  # from calibration.Rmd
# p <- c(0.58, 0.82, 0.99, 1.24)  # from calibration.Rmd
##     plot_res   n_sites   act_ext   eff_ext t_btwn_samp  act_dur   eff_dur
## 1: 0.5769693 0.3821107 0.7196559 0.4049972     1.01134 1.253045 0.5284913
##    plot_res n_sites  act_ext  eff_ext t_btwn_samp  act_dur  eff_dur
##       0.494   0.457    0.749    0.499       0.475    1.093    0.338
##    plot_res n_sites  act_ext  eff_ext t_btwn_samp  act_dur  eff_dur
##       0.577   0.382     0.72    0.405       1.045    1.261    0.643
p <- c(0.58, 0.72, 0.41, 1.05, 1.26, 0.64)  # from calibration.Rmd

@@

### Bootstrapped histograms (now main figure)
qtf <- function(x) c(mean(x), quantile(x, probs = c(0.025, 0.975))) # quant f
xlabs <- c("Spatial resolution", "Spatial extent", "Sampling interval", 
           "Temporal duration")
# axes <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
#              "tax1" = taxis1$logdays, "tax2" = taxis2$logdays)
axes2 <- list("aax1" = aaxis1$logres, "aax2" = aaxis2$logarea, 
              "tax1" = c(taxis2$logdays[-c(10:11)],
                         mean(taxis2$logdays[c(10:11)])), 
              "tax2" = taxis2$logdays)
axlabs <- list(alab1, alab2, tlab1[-10], tlab2)
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
# plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- 35
cols <- c(reds[c(4, 6)], blues[c(4, 6)])

@@

# pdf("paper/figures/hists_bs.pdf", width = 5, height = 5)
png("paper/figures/hists_bs.png", width = 5, height = 5, res = 600, 
    units = "in")
par(mfrow = c(2, 2), mar = c(4.5, 1, 1, 1), oma = c(2, 3, 0, 0))

@@

Statistics associated with Figure 1: percentage of observations falling within different scale ranges, and associated with different observational methods
```{r, eval = FALSE}
# res
# hdatst <- hdatstat[[1]]$density
hdatst <- hdatstat_bt$res$mu
l <- length(hdatst)
sum(hdatst[4:6])  # 53 % between 10cm^2 and 1 m^2
sum(hdatst[1:6])  #  67% < 1m^2
sum(hdatst[7:10]) # 24 % between 1 m^2 and 1 ha
sum(hdatst[11:(l)]) # 9 % 1-10000 ha
# dat[plot_res >= 10000^2]

@@

@@

# densities
# resolution
rres3 <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat3, 1)
rres3 <- (rres3 / cellStats(rres3, sum)) * 100

# extent
rext3 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat3, 1)
rext3 <- (rext3 / cellStats(rext3, sum)) * 100

@@

### Figure 3
```{r, eval=FALSE}
# actual versus effective duration
kdat <- bootp_dt  # bootstrap
# tempdat2 <- data.table(x = log10(kdat$act_dur), y = log10(kdat$eff_dur))
tempdat2 <- data.table(x = log10(kdat$eff_dur), y = log10(kdat$act_dur))
dinds <- kdat[, which(t_btwn_samp == 365 * 10000)]  # drop unreplicated obs
tempdat2 <- tempdat2[-dinds, ]
tempdat2 <- tempdat2[!is.na(x) & !is.na(y)] # cut out null values
tempdat2[, n := 1]  # set up count column
tx <- range(taxis2$logdays)
tx <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[x < tx[1], x := tx[1]]
tempdat2[x > tx[2], x := tx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[y < tx[1], y := tx[1]]
tempdat2[y > tx[2], y := tx[2]]
coordinates(tempdat2) <- ~x + y

@@

# Difference in effective versus actual extent/duration against actual ext/dur
hdat_bs2 <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  print(x)
  DT <- bootperturb[[x]]
  edb <- DT[, lapply(.SD, log10), .SDcol = c("eff_ext", "act_ext")]
  # edb <- edb[eff_ext >= act_ext, ]  # drop eff_dur < act
  setnames(edb, c("eff_ext", "act_ext"), c("eext", "aext"))
  edb[, dif := eext - aext]

  tdb <- DT[t_btwn_samp != 365 * 10000, lapply(.SD, log10), 
            .SDcol = c("eff_dur", "act_dur")]
  # tdb <- tdb[eff_dur >= act_dur, ]  # drop eff_dur < act
  setnames(tdb, c("eff_dur", "act_dur"), c("edur", "adur"))
  # print(paste(edb[, .N], tdb[, .N]))
  tdb[, dif := edur - adur]
  return(list("edb" = edb, "tdb" = tdb, #"elm" = elm, "tlm" = tlm, 
              "Ns" = c(edb[, .N], tdb[, .N])))
})

# calculate box statistics
# Extent differences
eint <- aaxis2$logarea
edif_int <- rbindlist(lapply(hdat_bs2, function(y) {  # y <- hdat_bs2[[2]]
  dd <- copy(y$edb[!is.na(aext)])
  dd[aext < ex[1], aext := ex[1]]  # set to min
  # dd[, list("int" = findInterval(aext, eint), "dif" = dif)]
  dd[, int := findInterval(aext, eint, rightmost.closed = TRUE)]
  # dd[, list("dif" = mean(dif, na.rm = TRUE), "N" = .N), by = int][order(int)]
}))
ints <- sort(edif_int[, unique(int)])
ebox <- lapply(ints, function(x) edif_int[int == x, lmisc::box_stats(dif)])
pctobs <- sapply(ints, function(x) edif_int[int == x, .N])
ewgt <- pctobs / sum(pctobs)
# ealphs <- (ewgt - min(ewgt)) / diff(range(ewgt))
ewgtint <- c(0, 1, 5, 10, 15, 20, 25) / 100  # weight intervals
ewgttxt <- c("  0", "  1", "  5", seq(10, 25, 5))
ecols <- findInterval(ewgt, ewgtint)  # corresponding color index

# temporal differences
dint <- taxis2$logdays[-5]
tx <- range(dint)
ddif_int <- rbindlist(lapply(hdat_bs2, function(y) {  # y <- hdat_bs2[[2]]
  dd <- copy(y$tdb[!is.na(adur)])
  dd[adur < tx[1], adur := tx[1]]  # set to min
  dd[adur > tx[2], adur := tx[2]]  # set to max
  dd[, int := findInterval(adur, dint, rightmost.closed = TRUE)]  # include high
}))
dints <- sort(ddif_int[, unique(int)])
tbox <- lapply(dints, function(x) ddif_int[int == x, lmisc::box_stats(dif)])
pctobs <- sapply(dints, function(x) ddif_int[int == x, .N])
dwgt <- pctobs / sum(pctobs)
# dalphs <- (dwgt - min(dwgt)) / diff(range(dwgt))
dwgtint <- c(0, 1, 5, 10, 15, 20, 25, 30) / 100  # weight intervals
dwgttxt <- c("  0", "  1", "  5", seq(10, 30, 5))
dcols <- findInterval(dwgt, dwgtint)

# y grid line function
ylines <- function(yr, by, lty = 1, col = "grey") {
  abline(h = seq.int(from = yr[1], to = yr[2], by = 2), lty = lty, col = col)
}

# pdf("paper/figures/act_v_eff_diff.pdf", width = 7, height = 4)
png("paper/figures/act_v_eff_diff.png", width = 7, height = 4, res = 600, 
    units = "in")
par(mfrow = c(1, 2), mar = c(4, 0, 1, 0.75), oma = c(0, 3, 0, 0))
bx <- rowMeans(cbind(eint[-length(eint)], eint[-1]))
# cols <- sapply(ealphs, function(x) rgb(0, 0.1, 1, alpha = x))
cols <- brewer.pal(length(ewgtint) - 1, "Blues")
plot(ex, c(0, 14), pch = "", xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     mgp = c(3, 0.5, 0), tcl = -0.2, xaxs = "i")
polygon(c(ex, rev(ex), ex[1]), c(-1, -1, 15, 15, -1), col = "grey90")
ylines(yr = c(0, 14), by = 2, col = "grey95")
for(i in 1:length(ebox)) {
  boxplot_v(bx[i], y = ebox[[i]], n = 1.75, whiskhgt = 1.5, 
            bfill = cols[ecols][i])
} 
axis(1, at = eint, labels = alab2, las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
axis(2, at = seq(0, 14, 2), las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
mtext("Actual Extent", side = 1, line = 3, cex = 0.9)
mtext("Difference Between", side = 2, line = 2.1, cex = 0.9)
mtext("Effective and Actual (Decades)", side = 2, line = 1.4, cex = 0.9)
lrng <- c(mean(ex), max(ex) - 0.05 * max(ex))
xs <- seq(lrng[1], lrng[2], by = (diff(lrng)) / (length(cols)))
rect_shade(xs, y = c(11.5, 12.5), fillcol = cols, linecol = "grey30")
text(xs, rep(10.5, length(xs)), ewgttxt, srt = 90, col = "grey30")
text(mean(xs), 13, "% of observations", col = "grey30")
mtext("A", side = 3, line = -1, cex = 1, adj = 0.05)

# duration
bx <- rowMeans(cbind(dint[-length(dint)], dint[-1]))
bd <- abs(dint[-length(dint)] - dint[-1])
# cols <- sapply(dalphs, function(x) rgb(1, 0, 0.1, alpha = x))
cols <- brewer.pal(length(dwgtint) - 1, "Reds")
plot(tx, c(0, 14), pch = "", xlab = "", ylab = "", xaxt = "n", xaxs = "i",
     mgp = c(3, 0.5, 0), tcl = -0.2, yaxt = "n")
polygon(c(tx, rev(tx), tx[1]), c(-1, -1, 15, 15, -1), col = "grey90")
ylines(yr = c(0, 14), by = 2, col = "grey95")
for(i in 1:length(tbox)) {
  boxplot_v(bx[i], y = tbox[[i]], n = 0.9, inhgt = bd[i] * 10, whiskhgt = 0.5, 
            bfill = cols[dcols][i])
} 
axis(1, at = dint, labels = tlab2[-c(5)], las = 2, tcl = -0.2, cex.axis = cxa, 
     mgp = c(3, 0.5, 0))
axis(2, at = seq(0, 14, 2), labels = rep("", 8), las = 2, tcl = -0.2, 
     cex.axis = cxa, mgp = c(3, 0.5, 0))
mtext("Actual Duration", side = 1, line = 3, cex = 0.9)
lrng <- c(mean(tx), max(tx) - 0.05 * max(tx))
xs <- seq(lrng[1], lrng[2], by = (diff(lrng)) / (length(cols)))
rect_shade(xs, y = c(11.5, 12.5), fillcol = cols, linecol = "grey30")
text(xs, rep(10.5, length(xs)), dwgttxt, srt = 90, col = "grey30")
text(mean(xs), 13, "% of observations", col = "grey30")
mtext("B", side = 3, line = -1, cex = 1, adj = 0.05)
dev.off()

# Kernel density version
pdf("paper/figures/act_v_eff.pdf", width = 7, height = 3)
par(mfrow = c(1, 2), mar = c(4.5, 4.5, 0.3, 3), oma = c(0, 0, 0.2, 1), 
    mgp = c(2, 0.25, 0))

@@

@@

```{r}
svars <- c("plot_res", "n_sites", "act_ext", "eff_ext", "samp_dur",
           "t_btwn_samp", "act_dur", "eff_dur")
sens <- gsub("\\\\", ";", dat$sensitivity)
sens <- gsub(", ", ";", gsub("; ", ";", sens))
sens <- tolower(sens)
sensl <- strsplit(sens, ";")
# unique(unlist(sensl))

sens2 <- gsub("plo_|plot-", "plot_", sens)  # fix this one
sens2 <- gsub("[[:blank:]]", "_", sens2)  # replace spaces with _
sens2 <- gsub("-", "_", sens2)  # replace - with _

corrtab <- cbind(c("^res", "plo_res", "plot_resolution", "plot_size", 
                   "sample_area", "samples_area", "sampled area", "study_area",
                   "sampled_area",
                   "t_btwn_samples", "t_btwn_sample", "t_btwn_samp_samp", 
                   "t_twn_samp", "t_btw_samp", "time_between_sampling", 
                   "time_between_samples", 
                   "samp_duratiion", "sampling_duration", "sample_duration", 
                   "number_of_sites", 
                   "study_span", "sutdy_span", "study_dur", "study_soan",
                   "samp_study", ":", " ", ";_", 
                   "duration", "dure", 
                   "extent"), 
                 c(rep("plot_res", 4), rep("act_ext", 5), rep("t_btwn_samp", 7),                    rep("samp_dur", 3), "n_sites", rep("eff_dur", 4), 
                   "samp;study", ";", ";", ";", 
                   "dur", "dur", "ext"))

# replace
for(i in 1:nrow(corrtab)) {
  sens2 <- gsub(corrtab[i, 1], corrtab[i, 2], sens2)
}
# gsub("[a-z]( )[a-z]", "_", sens[[228]])
# sens[[228]]
# sens2[is.na(sens2)]
sens2[is.na(sens2)] <- "none"
sensl2 <- lapply(1:length(sens2), function(x) strsplit(sens2[x], ";")[[1]])
# unique(unlist(sensl))
unique(unlist(sensl2))

# create a sensitivity table
senst <- do.call(cbind.data.frame, lapply(svars, function(x) {
  v <- sapply(sensl2, function(y) ifelse(any(y == x), 1, 0))
  # ifelse(is.na(v), 0, v)
}))
colnames(senst) <- c("res", "n", "aext", "eext", "sampd", "tbtwn", "actdur", 
                     "effdur")
